A convenient, flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate

### 2022-06-09 src/tex/ms.tex
[showyourwork] overleaf sync

We will now demonstrate the flexibility of our analytical model by systematically varying each of the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers.
To this end we use the publicly available simulations as presented in \cite{vanson+2022}
We use the framework described in detail in \cite{vanson+2022} that is part of the \COMPAS suite to compute local merger rates of BBH systems originating from

% We investigate the effect of the shape of the cosmic metallicity distribution on the local mass distribution of BBH mergers by systemically varying each of the variables that make up \dpdZ (first column of Table \ref{tab: fit params} and eq. \ref{eq: z log skew}).

>>>>

We will now demonstrate the flexibility of our analytical model by systematically varying each of the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers.
To this end we use the publicly available simulations as presented in \cite{vanson+2022}, consisting of rapid binary population synthesis using v02.19.04 of the \COMPAS suite \citep{COMPAS_method} \footnote{\url{https://compas.science/}}. 
We use the framework described in \cite{vanson+2022} to compute local merger rates of BBH systems originating from isolated binaries.

% that is part of the \COMPAS suite 
% We investigate the effect of the shape of the cosmic metallicity distribution on the local mass distribution of BBH mergers by systemically varying each of the variables that make up \dpdZ (first column of Table \ref{tab: fit params} and eq. \ref{eq: z log skew}).
